Analysis for Non-Expressive performances (DURATION)

### 2020-04-08 material/analysis/stim_n/ioi_duration.Rmd
add distribution plot and variability (CV)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
# read a filtered csv
df_onset <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".")
df_offset <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".")

# SubNr as a factor
df_onset$SubNr <- as.factor(df_onset$SubNr)
df_offset$SubNr <- as.factor(df_offset$SubNr)

# assign RowNr
df_onset$RowNr <- rep(1:72, nrow(df_onset)/72)
df_offset$RowNr <- rep(1:72, nrow(df_offset)/72)
```

```{r normDus, include = FALSE}
# extract trials which have both onset and offset data
df_onset$Eval <- "NA"
for (subnr in unique(df_offset$SubNr)){
  for (trial in unique(df_offset[SubNr == subnr]$Trial)){
    df_onset[SubNr == subnr & TrialNr == trial]$Eval <- "Yes"
  }
}
df_duration <- df_onset[Eval == "Yes"]

# check whether each row corresponds correctly
df_duration$Eval2 <- "NA"
for (i in 1:nrow(df_duration)){
  if (df_duration[i]$SubNr == df_offset[i]$SubNr & df_duration[i]$TrialNr == df_offset[i]$TrialNr & df_duration[i]$Pitch == df_offset[i]$Pitch){
    df_duration[i]$Eval2 <- "SAME"
  } else {
    df_duration[i]$Eval2 <- "DIFF"
  }
}
print(unique(df_duration$Eval2))

# calculate duration
df_duration$Duration <- df_offset$TimeStamp - df_duration$TimeStamp

# convert bpm to ms
df_duration[Tempo == 120]$Tempo <- 250
df_duration[Tempo == 110]$Tempo <- 273
df_duration[Tempo == 100]$Tempo <- 300

# normalised Duration
df_duration$normDu <- df_duration$Duration/df_duration$Tempo

# remove irrelevant intervals
ls_irrelevant <- list(c(27:28), c(33:35), 52, 57, c(66:72))
df_duration$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    df_duration[RowNr == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

```{r duration, echo = FALSE}
# For each individual
duration <- df_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr)]
print(duration)
```

### Plot
#### Bar chart
- Error bars show SD of the mean
- A dashed line represents the ideal tempo

@@

## Sequence plot
```{r seq, fig.width = 10, echo = FALSE}
# For each individual
duration_seq <- df_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), .(SubNr, RowNr)]

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, colour = SubNr)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width=.2,
                position = position_dodge(.05)) + 
  labs(x = "RowNr", y = "Normalised Duration") + scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq
```

@@

```{r duration_all, echo = FALSE}
# Group mean
duration_all <- df_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu))]
print(duration_all)
```

@@

```{r export, include = FALSE}
# export df_duration
write.csv(df_duration, file = "./data_duration.csv", row.names = F)
```

>>>>

```{r extract, include = FALSE}
# read a filtered csv
dt_onset <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".")
dt_offset <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".")

# SubNr as a factor
dt_onset$SubNr <- as.factor(dt_onset$SubNr)
dt_offset$SubNr <- as.factor(dt_offset$SubNr)

# assign RowNr
dt_onset$RowNr <- rep(1:72, nrow(dt_onset)/72)
dt_offset$RowNr <- rep(1:72, nrow(dt_offset)/72)
```

```{r normDus, include = FALSE}
# extract trials which have both onset and offset data
dt_onset$Eval <- "NA"
for (subnr in unique(dt_offset$SubNr)){
  for (trial in unique(dt_offset[SubNr == subnr]$Trial)){
    dt_onset[SubNr == subnr & TrialNr == trial]$Eval <- "Yes"
  }
}
dt_duration <- dt_onset[Eval == "Yes"]

# check whether each row corresponds correctly
dt_duration$Eval2 <- "NA"
for (i in 1:nrow(dt_duration)){
  if (dt_duration[i]$SubNr == dt_offset[i]$SubNr & dt_duration[i]$TrialNr == dt_offset[i]$TrialNr & dt_duration[i]$Pitch == dt_offset[i]$Pitch){
    dt_duration[i]$Eval2 <- "SAME"
  } else {
    dt_duration[i]$Eval2 <- "DIFF"
  }
}
print(unique(dt_duration$Eval2))

# calculate duration
dt_duration$Duration <- dt_offset$TimeStamp - dt_duration$TimeStamp

# convert bpm to ms
dt_duration[Tempo == 120]$Tempo <- 250
dt_duration[Tempo == 110]$Tempo <- 273
dt_duration[Tempo == 100]$Tempo <- 300

# normalised Duration
dt_duration$normDu <- dt_duration$Duration/dt_duration$Tempo

# remove irrelevant intervals
ls_irrelevant <- list(c(27:28), c(33:35), 52, 57, c(66:72))
dt_duration$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    dt_duration[RowNr == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

```{r duration, echo = FALSE}
# For each individual
duration <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr)]
print(duration)
```

### Plot
#### Bar chart
- Error bars show SD of the mean

@@

## Sequence plot
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Non-Expression") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq
```

## Distribution plot
```{r duration_dis, fig.width = 12, echo = FALSE}
p_duration_dis <- ggplot(dt_duration[EighthNote == "Yes"], aes(x = normDu)) +
  geom_histogram(binwidth=.1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Non-Expression")
p_duration_dis
```

@@

```{r duration_all, echo = FALSE}
# group mean
duration_all <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu))]
print(duration_all)
```

@@

```{r export, include = FALSE}
# export dt_duration
write.csv(dt_duration, file = "./data_duration.csv", row.names = F)
```

# Duration Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```
